MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex

\author[1]{Alexey Alekhin} \affil[1]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[2]{Evdokim Kovach} \affil[2]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[3]{Marina Manrique} \affil[3]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[4]{Pablo Pareja-Tobes} \affil[4]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[5]{Eduardo Pareja} \affil[5]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[6]{Raquel Tobes} \affil[6]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[7]{Eduardo Pareja-Tobes} \affil[7]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}

>>>>

% modified for this paper
\author[1]{Alexey Alekhin}
\author[1]{Evdokim Kovach}
\author[1]{Marina Manrique}
\author[1]{Pablo Pareja-Tobes}
\author[1]{Eduardo Pareja}
\author[1]{Raquel Tobes}
\author[1]{Eduardo Pareja-Tobes}
\affil[1]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
